---
title: "slide"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r echo=FALSE, message=FALSE}
setwd("/Users/Jimmy/Dropbox/stat133/final_proj/projects")
library("dplyr")
library("stringr")
library("MASS")
library("ggplot2")
library("plyr")
library("stringr")
library("readr")
library("reshape2")
library("png")

```

```{r echo=FALSE, message=FALSE}
# read in clean roster data
data_table = read.csv(file = "../data/cleandata/roster-salary-stats.csv" , header = TRUE, stringsAsFactors = FALSE)
data_table = data_table[, -1]

# read in Efficency data
EFF_table = read.csv(file = "../data/cleandata/eff-stats-salary.csv")

# add position column to Efficency table 
EFF_table$position = data_table$position


# read in summary table
summary_table = read.csv(file = "../data/cleandata/team-salaries.csv",
                         header = TRUE, stringsAsFactors = FALSE)

```

## test

```{r echo=FALSE, message=FALSE}

# bar plot for total pay roll for each team
ggplot(summary_table, aes(
  x = reorder(summary_table$X, summary_table$Total_Pay_Roll), y = summary_table$Total_Pay_Roll , fill =summary_table$X
  )) +
  geom_bar(stat = "identity") +
  labs(title = "NBA teams' Total Pay Roll ($)", x = "Team", y = "Total Pay Roll") +
  theme(axis.text.x = element_text(angle = 90,  hjust = 1 ))+
  guides(fill = guide_legend(title = "Team"))


```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

